---
title: "Run Models"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE, message = FALSE, warning = FALSE)
```
```{r}
library(R2WinBUGS)
library(mcmcplots)
```

You must have WinBUGS installed to fit the models. 

Running the models (example with CDEM only)

## CAR model data
```{r}
## CAR number of neighbors
num <- c(2,3,3,2,3,4,4,3,3,4,4,3,2,3,3,2)
##  CAR adjacency matrix
adj <- c(
  2,5,
  1,3,6,
  2,4,7,
  3,8,
  1,6,9,
  2,5,7,10,
  3,6,8,11,
  4,7,12,
  5,10,13,
  6,9,11,14,
  7,10,12,15,
  8,11,16,
  9,14,
  10,13,15,
  11,14,16,
  12,15
)
```


## 1) Logit-normal occupancy model with homogeneous detection
First run ONLY the CDEM data clean up chunk in `DataCleanUp.Rmd`. For other species, run their clean up chunk and revise the code below. 
```{r}
simple.data <- list(y = y)
## This creates the data in list form for Winbugs:
bugs.data(simple.data, dir = getwd(), data.file = "logit_data_CDEM.txt")

# initialize parameters
inits <- function(){list(
  p=runif(1,.2,.8), 
  c=runif(1,.5,1), 
  alpha0.mn=rnorm(1,1,1), 
  sig2.a1=runif(1,.01,3), 
  sig2.a0=runif(1,0.01,20))}

# run model
sim_CDEM_1h <- bugs(data="logit_data_CDEM.txt",
                  inits=inits, 
                  model.file="model_1a0h.txt", 
                  parameters=c("c", "p", "q", "alpha0.mn", "sig2.a1", "sig2.a0", "propz", "mu"), 
                  n.burnin=20000, 
                  n.thin=9, 
                  n.chains=3, 
                  n.iter=50000)  
```

Check convergence and save results
```{r}
sim_CDEM_1h$summary[c("c", "p", "q", "alpha0.mn","sig2.a1","sig2.a0"),]
denplot(sim_CDEM_1h,c("c", "p", "q", "alpha0.mn","sig2.a1","sig2.a0") )
traplot(sim_CDEM_1h,c("c", "p", "q", "alpha0.mn","sig2.a1","sig2.a0") )

save(sim_CDEM_1h, file="sim_CDEM_1h")
```

## 2) CAR occupancy model with homogeneous detection

```{r}
car.data <- list(y=y,  num=num, adj=adj)
## This creates the data in list form for Winbugs:
bugs.data(car.data, dir=getwd(), data.file="car_data_CDEM.txt")

# initialize parameters
inits <- function(){list(
  p=runif(1,.2,.8), 
  c=runif(1,.5,1), 
  alpha0.mn=rnorm(1,1,1), 
  sig2=runif(1,.01,6), 
  sig2.a0=runif(1,0.01,20))}
bugs.data(inits(),dir=getwd(),data.file="car_data_inits.txt")

# run model
sim_CDEM_2h <- bugs(
  data="car_data_CDEM.txt",
  inits=inits, 
  model.file="model_2a0h.txt", 
  parameters=c("c", "p", "q", "alpha0.mn","sig2.a0","sig2","propz","mu"), 
  n.burnin=20000, 
  n.thin=9, 
  n.chains=3, 
  n.iter=50000)  
```

Check convergence and save results
```{r}
sim_CDEM_2h$summary[c("c", "p", "q", "alpha0.mn","sig2","sig2.a0"),]
denplot(sim_CDEM_2h,c("c", "p", "q", "alpha0.mn","sig2","sig2.a0") )
traplot(sim_CDEM_2h,c("c", "p", "q", "alpha0.mn","sig2","sig2.a0") )

save(sim_CDEM_2h, file="sim_CDEM_2h")
```

## 3) CAR occupancy model with heterogeneous detection

```{r}
car.data <- list(y=y,  num=num, adj=adj)
## This creates the data in list form for Winbugs:
bugs.data(car.data, dir=getwd(), data.file="car_data_CDEM.txt")

# initialize parameters
inits <- function(){list(
  p=runif(1,.2,.8), 
  c=runif(34,.5,1), 
  alpha0.mn=rnorm(1,1,1), 
  sig2=runif(1,.01,6), 
  sig2.a0=runif(1,0.01,20))}
bugs.data(inits(),dir=getwd(),data.file="car_data_inits.txt")

# run model
sim_CDEM_3h <- bugs(
  data="car_data_CDEM.txt",
  inits=inits, 
  model.file="model_3a0h.txt", 
  parameters=c("c", "p", "q", "alpha0.mn","sig2.a0","sig2","propz","mu"), 
  n.burnin=20000, 
  n.thin=9, 
  n.chains=3, 
  n.iter=50000)  
```

Check convergence and save results
```{r}
sim_CDEM_3h$summary[c( "p",  "alpha0.mn","sig2","sig2.a0"),]
denplot(sim_CDEM_3h,c("p",  "alpha0.mn","sig2","sig2.a0") )
denplot(sim_CDEM_3h,c("c", "q"))
traplot(sim_CDEM_3h,c("p", "alpha0.mn","sig2","sig2.a0") )
traplot(sim_CDEM_3h,c("c", "q"))

save(sim_CDEM_3h, file="sim_CDEM_3h")
```

## 4) logit-normal occupancy model with heterogeneous detection

```{r}
simple.data <- list(y=y)
# This creates the data in list form for Winbugs:
bugs.data(simple.data, dir=getwd(), data.file="simple_data_CDEM.txt")

# initialize parameters
inits <- function(){list(
  p=runif(34,.2,.8), 
  c=runif(34,.5,1), 
  alpha0.mn=rnorm(1,1,1), 
  sig2.a1=runif(1,.01,3), 
  sig2.a0=runif(1,0.01,20))}

# run model
sim_CDEM_4h <- bugs(
  data="simple_data_CDEM.txt",
  inits=inits, 
  model.file="model_4a0h.txt", 
  parameters=c("c", "p", "q", "alpha0.mn","sig2.a1","sig2.a0","propz","mu"), 
  n.burnin=20000, 
  n.thin=9, 
  n.chains=3, 
  n.iter=50000)  
```

Check convergence and save results
```{r}
sim_CDEM_4h$summary[c( "p",  "alpha0.mn","sig2.a1","sig2.a0"),]
denplot(sim_CDEM_4h,c("p",  "alpha0.mn","sig2.a1","sig2.a0") )
denplot(sim_CDEM_4h,c("c", "q"))
traplot(sim_CDEM_4h,c("p", "alpha0.mn","sig2.a1","sig2.a0") )
traplot(sim_CDEM_4h,c("c", "q"))

save(sim_CDEM_4h, file="sim_CDEM_4h")
```
